---
title: 'Nucleotides developmental version'
author: "Christin"
date: "january 08, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup_knitr_general, include=FALSE}

opts_chunk$set(out.width = '\\linewidth')
opts_chunk$set(fig.align = 'center')
opts_chunk$set(fig.show = 'asis')

```

## Libaries, functions and Input

```{r Intro}

library(reshape2)
library(ggplot2)
library(RColorBrewer)
library(plyr)
library(scales)
library(magrittr)

source("Nucl_calibration_fcn.R")
```

## Calibration curves

### Import data 


```{r calibration_curves, fig.width=6, fig.height=5}
#### Import all required input files ---------------------------------
# Concentration levels of cal. curves
cal_conc = read.csv("level_conc_relation.csv", header = T)

# Annotation file calibration curve
nucl_names = read.csv("nucleotide_names_mapping.csv", header = T)

# Import calibration files incl. TrueBlanks
cal = import_files("input/calibrations/", 
                   mode = "cal",
                   conv_list = nucl_names, 
                   condition_list = cal_conc, 
                   plot_graph = TRUE)
```

### Evaluate calibration curves

Evaluation for:

  * Noise level
  * Saturation


```{r cal_evaluate}


```



## Sample files - Import and processing


```{r sample_proc}

#nucl_names = read.csv("nucleotide_names_mapping.csv", header = T)
annotation = read.csv("input/annotation.csv", TRUE)

#import samples data
samples = import_files("input/samples/", mode = "samples", 
                       conv_list = nucl_names,
                       condition_list = annotation,
                       plot_graph = TRUE)

```


```{r export_statistics}

### Correction of file names accordingly to Birtes sample list
conv_filenames = read.csv("input/annotation.csv", TRUE)
data_export = merge(nucl_sum, conv_filenames, all.x = TRUE)


##write a csv with intensities for all files (=technical replicates measured)
#write.csv(nucl_sum, "output/Sample_data.csv", row.names = FALSE)
write.csv(data_export, "output/Sample_data.csv", row.names = FALSE)

##summarises all technical replcates for one sample (max. 3 TR) and write a csv with averaged intensities for BRs
nucl_sum_summarised = summarySE(nucl_sum, measurevar = "mean", groupvars = c("file", "nuc"))

head(nucl_sum_summarised)

write.csv(nucl_sum_summarised, "output/Nucleotides_statistics.csv", row.names = FALSE)
```

## Next steps

Still required and missing:

  * Check for linearity range
  * Evaluation of transitions
  * Naming of batches: from A to batch1, ...
  * Levels change to dilutions
  * NucleoMixA corresponding to Quant1
  * Renaming: mean into mean_int